### 2025-08-25 SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd
adjusted the supplementary materials to reflect the new project structure, fixed references, and removed depricated files.

## Item origin & modifications
Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flake2022construct. The remaining nine were altered from the coding key to better fit the QMP counting operationalization. Because QMPs were aggregated they would need to have equivalent weighting in the importance of the overall QMP judgement of the protocol or article being evaluated.

All of the newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flake2020measurement. The information to report for each of the categories as presented in Table 1 in @flake2020measurement were used to determine what information there should be questions about in the protocol. However, feasibility of coding the information was also taken into account, and whether a lack of information could clearly be labelled as a QMP.

Two of the qualitative items have an equivalent in the coding key of Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flake2022construct. Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flake2022construct to be used for obtaining QMP ratios.

These (qualitative) variables assessed with two having an equivalent in @flake2022construct: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g. factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.

>>>>

## Item origin & modifications
Eleven out of twenty of the QMP variables used to calculate the QMP ratio have an equivalent in the coding key of @flakeConstructValidityValidity2022 The remaining nine were altered from the coding key to better fit the QMP counting operationalization. Because QMPs were aggregated they would need to have equivalent weighting in the importance of the overall QMP judgement of the protocol or article being evaluated.

All of the newly created or modified items were based on the definitions of the QMP categories and their criteria as specified in @flakeMeasurementSchmeasurementQuestionable2020 The information to report for each of the categories as presented in Table 1 in @flakeMeasurementSchmeasurementQuestionable2020 were used to determine what information there should be questions about in the protocol. However, feasibility of coding the information was also taken into account, and whether a lack of information could clearly be labelled as a QMP.

Two of the qualitative items have an equivalent in the coding key of Variables related to the specific measurement scaling and purpose in the paper, were omitted from the analyses of this study as they were deemed neither relevant for the analyses of this study, nor necessary in matching this study to the key results of @flakeConstructValidityValidity2022 Questions about more general measurement features such as the number of items and how scores were aggregated were altered from @flakeConstructValidityValidity2022 to be used for obtaining QMP ratios.

These (qualitative) variables assessed with two having an equivalent in @flakeConstructValidityValidity2022: the specific version of the measure (if reported); whether and what previous materials were used for the study; what, if any, psychometric evidence beyond reliability score (e.g. factor analysis, IRT model, convergent validity) was provided; and whether it was specified or not that the measure was or was not modified.

### 2025-08-25 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd
adjusted the supplementary materials to reflect the new project structure, fixed references, and removed depricated files.

<!-- Supplementary Analyses E -->

@@

# Supplementary Analyses E: Item Reduced Measures Analyses

This appendix contains analyses on the impact that measures with a changed number of items had on the results. These analyses were not pre-registered, but were conducted to check for the potentially confoudning influence of these measures. The results of these supplementary analyses show that this impact was minimal.

@@

```{r StoringItemReducedMeasureData}
# Storing the data on the Measures for which the number of items and/or response 
# options was altered from original to replication (of main interest are the
# measures for which the number of items were changed).
open_data(data = item_number_change_data, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(item_number_change_data))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(item_number_change_data))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(item_number_change_data))), ".yml"))

@@

# coding Unclear into No instead of Yes didn't make a difference on the test.
# hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "No"

@@

Interestingly, when item numbers decreased, the replicability seemed to have increased . Although the difference was not significant (`r decreased_items_replicability_impact_test_result`), and there were too few modifications to the items to get a stable estimate.

@@

```{r H1Difference}
# H1
coded_data_original_shortened$reliability_type[decreased_items_index]
coded_data_replications$reliability_type[decreased_items_index]
```

@@

```{r H2H3Difference}
# H2 & H3
coded_data_original_shortened$reliability_coeff[decreased_items_index]
coded_data_replications$reliability_coeff[decreased_items_index]

# running the H3 model
data_h3_avg[data_h3_avg$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]

@@

```{r OriginalQMPDIfference}
# comparing the mean and sd original QMP ratio 
print(c("mean decreased" = mean(data_h6$QMP_REV_ratio[decreased_items_index]),
      "sd decreased" = sd(data_h6$QMP_REV_ratio[decreased_items_index]),

      "mean non-decreased" = mean(data_h6$QMP_REV_ratio[-decreased_items_index]),
      "sd non-decreased" = sd(data_h6$QMP_REV_ratio[-decreased_items_index])))
```

@@

```{r OriginalQMPDIfference}
# comparing the mean and sd replication QMP ratio 
print(c("mean decreased" = mean(data_h6$Rep_QMP_REV_ratio[decreased_items_index]),
      "sd decreased" = sd(data_h6$Rep_QMP_REV_ratio[decreased_items_index]),

      "mean non-decreased" = mean(data_h6$Rep_QMP_REV_ratio[-decreased_items_index]),
      "sd non-decreased" = sd(data_h6$Rep_QMP_REV_ratio[-decreased_items_index])))
```

@@

```{r H4Difference}
# running the h4 models
# only decreased item measures
betareg_output_to_apa_full(betareg(QMP_REV_ratio ~ rep_org, data = data_h4[c(decreased_items_index, decreased_items_index),]))

# only non-decreased item measures
betareg_output_to_apa_full(betareg(QMP_REV_ratio ~ rep_org, data = data_h4[-c(decreased_items_index, decreased_items_index),]))

# all (originally)
betareg_output_to_apa_full(betareg(QMP_REV_ratio ~ rep_org, data = data_h4))
```

@@

```{r H5Difference}
# running the h5 models
apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5[decreased_items_index[c(53:55)],], family = binomial))$full_result$QMP_REV_ratio

apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5[-decreased_items_index[c(53:55)],], family = binomial))$full_result$QMP_REV_ratio

apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5, family = binomial))$full_result$QMP_REV_ratio

@@

```{r H6Difference}
# running the h6 models
betareg_output_to_apa_full(betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6[decreased_items_index,]))

betareg_output_to_apa_full(betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6[-decreased_items_index,]))

betareg_output_to_apa_full(betareg(Rep_QMP_REV_ratio ~ QMP_REV_ratio, data = data_h6))

>>>>

<!-- Supplementary Analyses C -->

@@

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(betareg)
library(statmod)
```

```{r data_prep}
# combine replication and original data 
is_replication <- c(rep(FALSE, 77), rep(TRUE, 77))

combi_org_rep <- rbind(coded_data_original, coded_data_replications)

combi_org_rep <- cbind(combi_org_rep, is_replication)

combi_org_rep$has_reliability <- combi_org_rep$reliability_type != "Not Reported" & combi_org_rep$reliability_type != ""

# function to calculate QMP ratios
calculating <- function(Data){
  QMP_data <- data.frame(def_ratio = rep(NA, 154),
                         op_ratio = rep(NA, 154),
                         sel_ratio = rep(NA, 154),
                         quant_ratio = rep(NA, 154),
                         mod_ratio = rep(NA, 154),
                         QMP_ratio = rep(NA, 154),
                         op_REV_ratio = rep(NA, 154),
                         sel_REV_ratio = rep(NA, 154),
                         quant_REV_ratio = rep(NA, 154),
                         mod_REV_ratio = rep(NA, 154),
                         QMP_REV_ratio = rep(NA, 154))

  def_count <- as.numeric(Data$def_1)
  def_count[is.na(def_count)] <- 0
  def_total <- as.numeric(!is.na(Data$def_1))
  QMP_data$def_ratio <- 1 - round(def_count / def_total, 4) 
  QMP_data$def_ratio[is.na(Data$def_ratio)] <- 0

  op_count <- rowSums(Data[16:20], na.rm = TRUE)
  op_total <- rowSums(!is.na(Data[16:20]))
  QMP_data$op_ratio <- 1 - round(op_count / op_total, 4)

  sel_count <- rowSums(Data[23:26], na.rm = TRUE)
  sel_total <- rowSums(!is.na(Data[23:26]))
  QMP_data$sel_ratio <- 1 - round(sel_count / sel_total, 4)

  quant_count <- rowSums(Data[29:32], na.rm = TRUE)
  quant_total <- rowSums(!is.na(Data[29:32]))
  QMP_data$quant_ratio <- 1 - round(quant_count / quant_total, 4)

  mod_count <- rowSums(Data[34:39], na.rm = TRUE)
  mod_total <- rowSums(!is.na(Data[34:39]))
  QMP_data$mod_ratio <- 1 - round(mod_count / mod_total, 4)

  MP_total <- def_total + op_total + sel_total + quant_total + mod_total
  MP_count <- def_count + op_count + sel_count + quant_count + mod_count
  QMP_data$QMP_ratio <- 1 - round(MP_count / MP_total, 4)

  op_REV_count <- rowSums(Data[c(18,19,41,42,43)], na.rm = TRUE)
  op_REV_total <- rowSums(!is.na(Data[c(18,19,41,42,43)]))
  QMP_data$op_REV_ratio <- 1 - round(op_REV_count / op_REV_total, 4)

  sel_REV_count <- rowSums(Data[c(24,26,44,45)], na.rm = TRUE)
  sel_REV_total <- rowSums(!is.na(Data[c(24,26,44,45)]))
  QMP_data$sel_REV_ratio <- 1 - round(sel_REV_count / sel_REV_total, 4)

  quant_REV_count <- rowSums(Data[c(32,48,49,50)], na.rm = TRUE)
  quant_REV_total <- rowSums(!is.na(Data[c(32,48,49,50)]))
  QMP_data$quant_REV_ratio <- 1 - round(quant_REV_count / quant_REV_total, 4)

  mod_REV_count <- rowSums(Data[52:57], na.rm = TRUE)
  mod_REV_total <- rowSums(!is.na(Data[52:57]))
  QMP_data$mod_REV_ratio <- 1 - round(mod_REV_count / mod_REV_total, 4)

  MP_REV_count <- def_count + op_REV_count + sel_REV_count + quant_REV_count + mod_REV_count
  MP_REV_total <- def_total + op_REV_total + sel_REV_total + quant_REV_total + mod_REV_total
  QMP_data$QMP_REV_ratio <- 1 - round(MP_REV_count / MP_REV_total, 4)

  return(QMP_data)
}

# calculating the QMP ratios for each QMP item.
QMP_Ratio_data <- calculating(combi_org_rep)

QMP_Ratio_data <- cbind(QMP_Ratio_data, is_replication)

# Supplementary Analyses C: Item Reduced Measures Analyses

This appendix contains the analyses on the impact that measures with a changed number of items had on the main results from  Supplementary Analyses A. These analyses were not pre-registered, but were conducted to check for the potentially confounding influence of these measures. The results of these supplementary analyses show that this impact was minimal overall.

@@

@@

@@

Interestingly, when item numbers decreased, the replicability seemed to have increased. Although the difference was not significant (`r decreased_items_replicability_impact_test_result`), and there were too few modifications to the items to get a stable estimate.

@@

```{r H1Difference}
# H1
coded_data_original$reliability_type[decreased_items_index]
coded_data_replications$reliability_type[decreased_items_index]
```

@@

```{r H2H3Difference}
# H2 & H3
coded_data_original$reliability_coeff[decreased_items_index]
coded_data_replications$reliability_coeff[decreased_items_index]

# running the H3 model
measure_reliability_data[measure_reliability_data$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]

@@

```{r OriginalQMPDIfference}
# first we combine the datasets of the original studies and the replications 
# together
# adding "Rep_" to separate replication from original columns in the combined dataset
data_h4_Rep <- QMP_Ratio_data[QMP_Ratio_data$is_replication,]
colnames(data_h4_Rep) <- paste0("Rep_", colnames(data_h4_Rep))

# combine the dataset
data_h4 <- cbind(QMP_Ratio_data[!QMP_Ratio_data$is_replication,], data_h4_Rep)

# comparing the mean and sd original QMP ratio 
print(c("mean decreased" = mean(data_h4$QMP_REV_ratio[decreased_items_index]),
      "sd decreased" = sd(data_h4$QMP_REV_ratio[decreased_items_index]),

      "mean non-decreased" = mean(data_h4$QMP_REV_ratio[-decreased_items_index]),
      "sd non-decreased" = sd(data_h4$QMP_REV_ratio[-decreased_items_index])))
```

@@

```{r ReplicationQMPDIfference}
# comparing the mean and sd replication QMP ratio 
print(c("mean decreased" = mean(data_h4$Rep_QMP_REV_ratio[decreased_items_index]),
      "sd decreased" = sd(data_h4$Rep_QMP_REV_ratio[decreased_items_index]),

      "mean non-decreased" = mean(data_h4$Rep_QMP_REV_ratio[-decreased_items_index]),
      "sd non-decreased" = sd(data_h4$Rep_QMP_REV_ratio[-decreased_items_index])))
```

@@

```{r H4Difference}
# for H4 we have to combine the replication and original data together
data_h4 <- rbind(data_h456_original, data_h456_replications)

# running the h4 models
# only decreased item measures
betareg(QMP_REV_ratio ~ is_replication, data = QMP_Ratio_data[decreased_items_index,])

# only non-decreased item measures
betareg(QMP_REV_ratio ~ is_replication, data = QMP_Ratio_data[!decreased_items_index,])

# all (originally)
betareg(QMP_REV_ratio ~ is_replication, data = QMP_Ratio_data)

@@

```{r H5Difference}
## running the h5 models
# first making data with and without decreased item measures
Diff_QMP_Ratio_data <- QMP_Ratio_data[QMP_Ratio_data$is_replication,]
Diff_QMP_Ratio_data <- Diff_QMP_Ratio_data[decreased_items_index,]
UnDiff_QMP_Ratio_data <- QMP_Ratio_data[QMP_Ratio_data$is_replication,]
UnDiff_QMP_Ratio_data <- UnDiff_QMP_Ratio_data[-decreased_items_index,]
Diff_coded_data_replications <- coded_data_replications[decreased_items_index,]
UnDiff_coded_data_replications <- coded_data_replications[-decreased_items_index,]

# running the model using the QMPs from the revised coding protocol
betareg(Diff_QMP_Ratio_data$QMP_REV_ratio ~ Diff_coded_data_replications$hypothesis_support)

betareg(UnDiff_QMP_Ratio_data$QMP_REV_ratio ~ UnDiff_coded_data_replications$hypothesis_support)

betareg(QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_REV_ratio ~ coded_data_replications$hypothesis_support)
```

@@

```{r H6Difference}
# running the h6 models
betareg(QMP_Ratio_data[!QMP_Ratio_data$is_replication,]$QMP_REV_ratio[decreased_items_index] ~ QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_REV_ratio[decreased_items_index])

betareg(QMP_Ratio_data[!QMP_Ratio_data$is_replication,]$QMP_REV_ratio[!decreased_items_index] ~ QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_REV_ratio[!decreased_items_index])

betareg(QMP_Ratio_data[!QMP_Ratio_data$is_replication,]$QMP_REV_ratio ~ QMP_Ratio_data[QMP_Ratio_data$is_replication,]$QMP_REV_ratio)

### 2025-08-25 SupplementaryMaterials/data_retrieval_information.Rmd
adjusted the supplementary materials to reflect the new project structure, fixed references, and removed depricated files.

# plot of the multilevel data structure
ggplot(plot_data_structure_data, aes(x = N, y = factor(many_labs_version, levels = c("5", "3", "2", "1")), 
                                colour = rep_org, shape = hypothesis_support, size = measure_count)) +
  geom_point(alpha = .33) +

>>>>

full_coded_data <- rbind(coded_data_original, coded_data_replications)

plot_data_structure_data <- data.frame()

for (i in 1:nrow(full_coded_data)){
  if(full_coded_data$variable_order[i] == 1){
    plot_data_structure_data <- rbind(plot_data_structure_data, full_coded_data[i,])
  }

  if(full_coded_data$variable_order[i] != 1){
    plot_data_structure_data[nrow(plot_data_structure_data),] <- full_coded_data[i,]
  }
}

# plot of the multilevel data structure
ggplot(plot_data_structure_data, aes(x = N, y = factor(many_labs_version, levels = c("5", "3", "2", "1")), 
                                colour = rep_org, shape = hypothesis_support, size = variable_order)) +
  geom_point(alpha = .33) +
